---
title: "Developing Data Products Week 3 Project"
author: "Charles Smith"
date: "January 6, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Synopsis

Project Instructions:

- Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities.
- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

My plot is a multi-line plot showing population growth of the four (currently) most populous states in the United States - California, Florida, New York, and Texas.  It uses U.S. Census data from 1900 - 2010.

## State Population Growth 1900 - 2010

```{r, echo=FALSE, message = FALSE, warning=FALSE}
library(plotly)
stateDf <- read.csv("uscensus.csv")
```
```{r, fig.align="center", message = FALSE, warning=FALSE}
plot_ly(stateDf, x = ~Year, y= ~Population,
        color = ~State, mode="lines")
```
